Formalizing Stack Safety as a Security Property

### 2021-09-08 submission3/main.tex
More small fixes

We use these properties to validate the stack-safety {\em micro-policies}
proposed by~\citet{DBLP:conf/sp/RoesslerD18}.  Specifically, we check (with
property-based random testing) that Roessler and DeHon's ``eager''
micro-policy, which catches violations as early as possible, enforces a
simple ``stepwise'' variant of our properties and correctly, and that
(a repaired version of) their more performant
``lazy'' micro-policy enforces a slightly weaker and more extensional
observational property. Meanwhile our testing successfully detects violations
in several broken variants, including Roessler and DeHon's original lazy policy.

@@

\begin{itemize}
\item We adapt concepts of integrity and confidentiality from language-based
security, combine these with an existing notion of well-bracketed
control flow to formalize a {\em stepwise stack-safety}
property, and argue that this property captures the intuitive concept of
strict stack
safety~(\cref{sec:prelim,sec:lse}).
\item We use property-based random testing to check that this stepwise
property is actually enforced by the {\em Depth Isolation} policy
of~\citet{DBLP:conf/sp/RoesslerD18}; in the process, we extend the generation by
execution techniques of \citet{TestingNI:ICFP} to handle nested
properties (\cref{sec:enforcement}).
\item We formalize weaker but more extensional \emph{observational} variants of
  confidentiality and integrity. Both are parameterized over a notion of external
  observation, and are violated only if the accessing of secrets or overwriting of
  data later causes a visible change in the system behavior (\cref{sec:lazy}).
\item We show that the definition can be
extended to argument passing on the stack, callee-saves registers, and a simple coroutine system (\cref{sec:ext}).
\end{itemize}
\Cref{sec:relwork,sec:future} discuss related and future work.

@@

This is the set of all possible calls that be reached from any well-formed initial state.

>>>>

We use these properties to validate the stack-safety {\em micro-policies}
proposed by~\citet{DBLP:conf/sp/RoesslerD18}.  Specifically, we check (with
property-based random testing) that Roessler and DeHon's ``eager''
micro-policy, which catches violations as early as possible, enforces a
simple ``stepwise'' variant of our properties, and that
(a repaired version of) their more performant
``lazy'' micro-policy enforces a slightly weaker and more extensional
observational property. Meanwhile our testing successfully detects violations
in several broken variants, including Roessler and DeHon's original lazy policy.

@@

\begin{itemize}
\item We adapt concepts of integrity and confidentiality from language-based
security, combine these with an existing notion of well-bracketed
control flow to formalize a {\em stepwise stack-safety}
property, and which captures the intuitive concept of
strict stack safety enforced over each step of execution~(\cref{sec:prelim,sec:lse}).
\item We use property-based random testing to check that this stepwise
property is actually enforced by the {\em Depth Isolation} policy
of~\citet{DBLP:conf/sp/RoesslerD18}; in the process, we extend the generation by
execution techniques of \citet{TestingNI:ICFP} to handle nested
properties (\cref{sec:enforcement}).
\item We formalize weaker but more extensional \emph{observational} variants of
  confidentiality and integrity. Both are parameterized over a notion of external
  observation, and are violated only if the accessing of secrets or overwriting of
  data later causes a visible change in the system behavior (\cref{sec:lazy}).
\item We show that the definition can be
extended to argument passing on the stack, callee-saves registers, and a simple coroutine system (\cref{sec:ext}).
\end{itemize}
\Cref{sec:relwork,sec:future} discuss related and future work.

@@

This is the set of all possible calls that can be reached from any well-formed initial state.
